Regular singular Volterra equations on complex domains

### 2023-08-17 reg-sing-volterra.tex
Work on cond:diag-basic and cond:eps-lambda in example
Flag failure of cond:eps-lambda in general case. Mention that cond:slow isn't
needed.

@@

Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
\[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:
\begin{conditions}
\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---the {\em residue} of the singularity---the difference
\[ \hardker(a, a') - \frac{\tau}{\zeta(a)} \]
is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
\end{conditions}
We'll assume that $\tau$ is real and positive.

@@

To apply Theorem~\ref{thm:general_volterra}, we need to rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting}. \textcolor{orange}{[Explain how conditions shift from $\zeta = 0$ to $\zeta = \alpha$?]} When we write $\hat{\mathcal{P}}_\alpha$ explicitly as a Volterra operator, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0, \]
where
\[ k_R(a,a')=\sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{R_{r,j}}{j!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} \, \big(-\zeta(a')\big)^r. \]
Isolating $p\,\varphi$ on the left and dividing both sides by $p$ yields the equivalent equation
\begin{equation}\label{eqn:divided}
\varphi(a) = -\int_{\zeta=\alpha}^a \frac{q}{p(a)} \, \varphi \; d\zeta - \int_{\zeta=\alpha}^a \frac{k_R(a,\cdot)}{p(a)} \, \varphi \, d\zeta.
\end{equation}
Let $\hardpart^\alpha$ be the Volterra operator with kernel
\[ \hardker^\alpha(a,a') = -\frac{q(a')}{p(a)}, \]
and let $\softpart^\alpha$ be the Volterra operator with kernel
\[ \softker^\alpha(a,a') = -\frac{k_R(a,a')}{p(a)}. \]
Now we can write Equation~\eqref{eqn:divided} as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.

The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$. One part of this observation demands some explanation: we need to confirm that the power series defining $k_R$ converges everywhere. To do this, recall that the functions $R_r(z^{-1})$ are all holomorphic on the disk $|z| > A$. Consequently, for any $\lambda > A$, we have $R_{r,j} \lesssim \lambda^j$ over all $r \in \{1, \ldots, d-1\}$ and all $j \in \{0, 1, 2, \ldots\}$. This is enough to show that $k_R$ is well-defined throughout $\C^2$. In fact, as we'll see later, it also leads to a useful bound on $k_R$.
\begin{verify}
\begin{align*}
& \sum_{j = 0}^\infty R_{r,j} z^{-j} \text{ converges when } |z| > A \\
\Longrightarrow & \sum_{j = 0}^\infty R_{r,j} z^{-j} \text{ converges when } |z^{-1}| < A^{-1} \\
\Longrightarrow & A^{-1} \le \operatorname{radius} R_{r,j} \\
\Longrightarrow & A \ge \big(\operatorname{radius} R_{r,j}\big)^{-1} \\
\Longrightarrow & A \ge \limsup_{j \to \infty} R_{r,j}^{1/j} \\
\Longrightarrow & A \ge \inf_{J \ge 0} \sup_{j \ge J} R_{r,j}^{1/j} \\
\Longrightarrow & \forall \lambda > A: \exists J: \sup_{j \ge J} R_{r,j}^{1/j} < \lambda \\
\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_{r,j}^{1/j} < \lambda \\
\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_{r,j} < \lambda^j
\end{align*}
\end{verify}

Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we're now working in the setting of Theorem~\ref{thm:general_volterra}. To apply the theorem, we just need to show that $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.
\begin{itemize}
\item Condition~\eqref{cond:sing} {\em on $\hardpart^\alpha$ is satisfied}.

Since $P$ is a monic polynomial whose roots are all simple, $1/P(-\zeta)$ has the nice partial fraction decomposition
\[ \frac{1}{P(-\zeta)} = \sum_{-\beta \in \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
where $\roots$ is the zero set of $P$ \textcolor{orange}{[Ahlfors, {\em Complex Analysis}, \S1.4, Exercise~2]}. 
It follows that
\begin{align*}
-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}
\end{align*}
As $a$ and $a'$ approach $\zeta = \alpha$, the
\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \]
part approaches the limit
\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\alpha)}{P'(-\beta)\,(\alpha - \beta)}. \]
Hence, that part is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$. Now we just have to deal with the term
\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a)-\alpha)}. \]
%%From the fact that
%%\[ Q(-\zeta) \in Q(-\alpha) + O\big(|\zeta - \alpha|\big) \]
%%at $\zeta = \alpha$, we reason that
%%\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a)-\alpha)} \in \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a)-\alpha)} + O(1) \]
%%at $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$.

@@

is bounded as $a,a'$ approach $\zeta=\alpha$.
\begin{verify}
\par Proof of Ahlfors exercise. First, observe that
\begin{align*}
P(t) &= (t + \beta_1) \cdots (t + \beta_d) \\
P'(t) &= \sum_k \left[ \prod_{j \neq k} (t + \beta_j) \right] \\
P'(-\beta_1) &= \prod_{j\neq 1} (-\beta_1 + \beta_j) 
\end{align*}
Then we see that
\begin{align*}
\frac{1}{P(t)} & = \sum_{j} \frac{\pi_j}{t + \beta_j}\\
-\frac{P'(t)}{P(t)^2} &= -\sum_{j} \frac{\pi_\beta}{(t + \beta_j)^2}\\
P'(t) &= \sum_{j} \pi_j \left(\frac{P(t)}{t + \beta_j}\right)^2\\
P'(-\beta_1) &=  \pi_1 \prod_{j\neq 1} (-\beta_1+\beta_j)^2\\
\frac{1}{P'(-\beta_1)} &= \pi_1
\end{align*}
\end{verify}
\end{itemize}

\par\color{RoyalBlue}
Notice that $\hardpart^\alpha$ is holomorphic and separable, while $\softpart^\alpha$ is holomorphic and non-separable. In addition, $\hardpart^\alpha$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by Taylor expanding the polynomials $p$ and $q$ around $\zeta = \alpha$ \textcolor{orange}{[the shifted polynomial will have the same degree as the original]} \textcolor{magenta}{[$\alpha$ is a number, not a point; write $c_0$ in place of $q(\alpha)$? notation $\zeta'$ not defined; switch to $\zeta(a')$?]}.
\begin{align*}
    -\frac{q}{p(a)}&=-\frac{\textcolor{magenta}{q(\alpha)}+c_1(\zeta\textcolor{magenta}{'}-\alpha)+c_2 (\zeta'-\alpha)^2+...}{-b_1(\zeta(a)-\alpha)+ b_2 (\zeta(a)-\alpha)^2+b_3(\zeta(a)-\alpha)^3+...}\\
    &=\frac{q(\alpha)}{b_1(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+ b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}\\
    &=\frac{q(\alpha)}{b_1(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}
\end{align*}
hence setting $\tau_\alpha:=\textcolor{magenta}{-}\frac{q}{p'}\textcolor{orange}{\big|_{\zeta = \alpha}}\neq 0$, we find
\begin{equation*}
    -\frac{q(a')}{p(a)}-\frac{\tau_\alpha}{\zeta(a)-\alpha}
\end{equation*}
is bounded as $\zeta(a')$ and $\zeta(a)$ approach $\alpha$.
\color{black}
\par\color{SkyBlue}
Since $p$ has only simple roots, the partial fraction decomposition of $1/p$ is
\[ \sum_{\beta \in \roots} \left.\frac{1}{p'}\right|_{\zeta = \beta} \frac{1}{\zeta - \beta}, \]
where $\roots$ is the set containing the values of $\zeta$ at the roots of $p$.
\par\color{DarkTurquoise}
\textcolor{orange}{Nicer formulation; note different definition of $\roots$:}\par

\color{black}

Then, the proof will follow by Theorem \ref{thm:general_volterra}, once we proved that $\volterra^\alpha$ satisfies the required assumptions.

\begin{enumerate}
    \item[$\bullet$] $\hardpart^\alpha$ satisfies Condition \eqref{cond:slow}: by assumption $p$ and $q$ are polynomials, and $q$ has degree less that $p$. Hence for $a$ outside some neighbourhood $U$ of $\alpha$  
\begin{align*}
    \sup_U \Big\vert \frac{1}{p}\Big\vert =:c_p \qquad\qquad \sup_U \Big\vert\frac{q}{p}\Big\vert =:\lambda_\text{ration} 
\end{align*}
    and we set $\lambda_0:=\log(c_p)+\lambda_\text{ratio}$. 
    \item[$\bullet$] $\hardpart^\alpha$ satisfies Condition \eqref{cond:diag-basic}: in fact $p$ and $q$ are polynomials and $q$ has degree less than $p$, hence their ratio is exponentially bounded if $\zeta(a), \zeta(a')$ are far from $\alpha$. In particular, $\lambda_\Delta=2A$ is a possible choice, where $A$ is the radius of convergence of the functions $R_r$ (see \ref{sec:level 1 ODE}).    
    \item[$\bullet$]  $\softpart^\alpha$ satisfies Condition \eqref{cond:eps-lambda}: recall that all functions $R_r(z^{-1})$ are holomorphic for $|z|>A$,

    \begin{align*}
        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^j}{|p(\zeta(a))|}|\zeta(a')|^r  &\lesssim \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(\zeta(a))|}|\zeta(a')|^r \\
        & \lesssim |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(\zeta(a))|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
        &\lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
        &\lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
    \end{align*}
now we notice that $\Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert$ is bounded for $a,a'$ far from $\alpha$ by the argument we use in the proof of Condition \eqref{cond:diag-basic}. If $\zeta(a), \zeta(a')$ are close to $\alpha$ we can use Condition \eqref{cond:sing}

@@

and $\gamma=1$.

Finally, to get the result as stated, we need to show that
\[ f_{0, \alpha} \in M\zeta^{\tau_\alpha - 1} + \singexpalg{\tau_\alpha}(\domain_\alpha) \]
for some constant $M$. Like in the proof of Proposition \ref{prop:alt-general_volterra}, it's enough to show that $p$ satisfies Condition \eqref{cond:reg-p} with $\epsilon=1$. Since $p$ is a polynomial with a simple zero at $\zeta=\alpha$, we have that

>>>>

\item Deal with Condition~\eqref{cond:sing}
\item In Section~\ref{sec:V is a contraction}, do we only use Condition~\eqref{cond:sing} through Proposition~\ref{prop:whole-ker-near-bound}?

@@

Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
\[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:
\begin{conditions}
\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---the {\em residue} of the singularity---the difference
\[ \hardker(a, a') - \frac{\tau}{\zeta(a)} \]
\textcolor{magenta}{\[ \zeta(a)\hardker(a, a') - \tau \]}
is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
\end{conditions}
We'll assume that $\tau$ is real and positive.

@@

To apply Proposition~\ref{prop:alt-general_volterra}, we need to rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting}. \textcolor{orange}{[Explain how conditions shift from $\zeta = 0$ to $\zeta = \alpha$?]} When we write $\hat{\mathcal{P}}_\alpha$ explicitly as a Volterra operator, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0, \]
where
\[ k_R(a,a')=\sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{R_{r,j}}{j!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} \, \big(-\zeta(a')\big)^r. \]
Isolating $p\,\varphi$ on the left and dividing both sides by $p$ yields the equivalent equation
\begin{equation}\label{eqn:divided}
\varphi(a) = -\int_{\zeta=\alpha}^a \frac{q}{p(a)} \, \varphi \; d\zeta - \int_{\zeta=\alpha}^a \frac{k_R(a,\cdot)}{p(a)} \, \varphi \, d\zeta.
\end{equation}
Let $\hardpart^\alpha$ be the Volterra operator with kernel
\[ \hardker^\alpha(a,a') = -\frac{q(a')}{p(a)}, \]
and let $\softpart^\alpha$ be the Volterra operator with kernel
\[ \softker^\alpha(a,a') = -\frac{k_R(a,a')}{p(a)}. \]
Now we can write Equation~\eqref{eqn:divided} as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.

The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$. One part of this observation demands some explanation: we need to confirm that the power series defining $k_R$ converges everywhere. To do this, recall that the functions $R_r(z^{-1})$ are all holomorphic on the disk $|z| > A$. Consequently, for any $\lambda > A$, we have $|R_{r,j}| \lesssim \lambda^j$ over all $r \in \{1, \ldots, d-1\}$ and $j \in \{0, 1, 2, \ldots\}$. This is enough to show that $k_R$ is well-defined throughout $\C^2$. In fact, as we'll see later, it also leads to a useful bound on $k_R$.
\begin{verify}
\begin{align*}
& \sum_{j = 0}^\infty R_{r,j} z^{-j} \text{ converges when } |z| > A \\
\Longrightarrow & \sum_{j = 0}^\infty R_{r,j} z^{-j} \text{ converges when } |z^{-1}| < A^{-1} \\
\Longrightarrow & A^{-1} \le \operatorname{radius} R_{r,j} \\
\Longrightarrow & A \ge \big(\operatorname{radius} R_{r,j}\big)^{-1} \\
\Longrightarrow & A \ge \limsup_{j \to \infty} R_{r,j}^{1/j} \\
\Longrightarrow & A \ge \inf_{J \ge 0} \sup_{j \ge J} R_{r,j}^{1/j} \\
\Longrightarrow & \forall \lambda > A: \exists J: \sup_{j \ge J} R_{r,j}^{1/j} < \lambda \\
\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_{r,j}^{1/j} < \lambda \\
\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_{r,j} < \lambda^j
\end{align*}
\end{verify}

Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we're now working in the setting of Proposition~\ref{prop:alt-general_volterra}. To apply the theorem, we just need to show that $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.
\begin{itemize}
\item Condition~\eqref{cond:sing} {\em on $\hardpart^\alpha$ is satisfied.}

Since $P$ is a monic polynomial whose roots are all simple, $1/P(-\zeta)$ has the nice partial fraction decomposition
\[ \frac{1}{P(-\zeta)} = \sum_{-\beta \in \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
where $\roots$ is the zero set of $P$ \cite[Section 1.4, Exercise~2]{ahlfors}. 
It follows that
\begin{align*}
-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}
\end{align*}
As $a$ and $a'$ approach $\zeta = \alpha$, the
\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \]
part approaches the limit
\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\alpha)}{P'(-\beta)\,(\alpha - \beta)}. \]
Hence, that part is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$. Now we just have to deal with the term
\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a)-\alpha)}. \]
%%From the fact that
%%\[ Q(-\zeta) \in Q(-\alpha) + O\big(|\zeta - \alpha|\big) \]
%%at $\zeta = \alpha$, we reason that
%%\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a)-\alpha)} \in \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a)-\alpha)} + O(1) \]
%%at $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$.

@@

is bounded as $a,a'$ approach $\zeta=\alpha$.
\begin{verify}
\par Proof of Ahlfors exercise. First, observe that
\begin{align*}
P(t) &= (t + \beta_1) \cdots (t + \beta_d) \\
P'(t) &= \sum_k \left[ \prod_{j \neq k} (t + \beta_j) \right] \\
P'(-\beta_1) &= \prod_{j\neq 1} (-\beta_1 + \beta_j) 
\end{align*}
Then we see that
\begin{align*}
\frac{1}{P(t)} & = \sum_{j} \frac{\pi_j}{t + \beta_j}\\
-\frac{P'(t)}{P(t)^2} &= -\sum_{j} \frac{\pi_\beta}{(t + \beta_j)^2}\\
P'(t) &= \sum_{j} \pi_j \left(\frac{P(t)}{t + \beta_j}\right)^2\\
P'(-\beta_1) &=  \pi_1 \prod_{j\neq 1} (-\beta_1+\beta_j)^2\\
\frac{1}{P'(-\beta_1)} &= \pi_1
\end{align*}
\end{verify}
\color{Tan}
\item \textcolor{orange}{[Condition~\eqref{cond:diag-basic} implies Condition~\eqref{cond:slow}, so we can drop this.]}

$\hardpart^\alpha$ satisfies Condition \eqref{cond:slow}: by assumption $p$ and $q$ are polynomials, and $q$ has degree less that $p$. Hence for $a$ outside some neighbourhood $U$ of $\alpha$  
\begin{align*}
\sup_U \Big\vert \frac{1}{p}\Big\vert =:c_p \qquad\qquad \sup_U \Big\vert\frac{q}{p}\Big\vert =:\lambda_\text{ration} 
\end{align*}
and we set $\lambda_0:=\log(c_p)+\lambda_\text{ratio}$.
\color{black}
\item Condition~\eqref{cond:diag-basic} {\em on $\hardpart^\alpha$ is satisfied.}

Since we're trying to bound $\hardker^\alpha(a, a')$ with a function of the difference $\omega(a, a') := \zeta(a) - \zeta(a')$, let's rewrite it as a rational function of $\omega(a, a')$ and $\zeta(a)$. First, rewrite
\begin{align*}
q(a') & = Q\big(-\zeta(a')\big) \\
& = Q\big(\omega(a, a') - \zeta(a)\big)
\end{align*}
in the form
\[ q(a') = Q_{d-1}\big(\zeta(a)\big)\;\omega(a, a')^{d-1} + \ldots + Q_1\big(\zeta(a)\big)\;\omega(a, a') + Q_0\big(\zeta(a)\big), \]
where $Q_0, \ldots Q_{d-1}$ are polynomials of degree at most $d-1$. We can then write $-\hardker^\alpha(a, a')$ in the form
\[ \frac{q(a')}{p(a)} = \frac{Q_{d-1}\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}\;\omega(a, a')^{d-1} + \ldots + \frac{Q_1\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}\;\omega(a, a') + \frac{Q_0\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}, \]
viewing it as a polynomial in $\omega(a, a')$ whose coefficients are rational functions in $\zeta(a)$. If we keep $a$ away from the roots of from the roots of $p$, each coefficient is bounded, so $|\hardker^\alpha(a, a')|$ is bounded by a polynomial in $|\omega(a, a')|$. It follows that for any $\lambda_\Delta > 0$, we have
\[ |\hardker^\alpha(a, a')| \lesssim e^{\lambda_\Delta|\omega(a, a')|} \]
over all $a$ outside a neighborhoood of the roots of $p$ and all $a'$ without restriction.

For consistency with Condition~\eqref{cond:eps-lambda}, we choose $\lambda_\Delta > A$.
\color{RoyalBlue}
\item $\hardpart^\alpha$ satisfies Condition \eqref{cond:diag-basic}: in fact $p$ and $q$ are polynomials and $q$ has degree less than $p$, hence their ratio is exponentially bounded if $\zeta(a), \zeta(a')$ are far from $\alpha$. In particular, $\lambda_\Delta=2A$ is a possible choice, where $A$ is the radius of convergence of the functions $R_r$ (see \ref{sec:level 1 ODE}).
\color{black}
\item Condition~\eqref{cond:eps-lambda} {\em on $\softpart^\alpha$ is satisfied.} \textcolor{magenta}{[I think this bound fails unless $R_1, \ldots, R_{d-1}$ are zero, so let's restrict our attention to that case.]}

First, obseve that
\begin{align*}
|\softker^\alpha(a, a')| & = \left|\frac{k_R(a, a')}{p(a)}\right| \\
& \le \frac{1}{|p(a)|} \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{|R_{r,j}|}{j!} \, |\zeta(a)-\zeta(a')|^{j+1} |\zeta(a')|^r \\
& = \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} \sum_{r=0}^{d-1} |\zeta(a')|^r \sum_{j=0}^\infty \frac{|R_{r,j}|}{j!} \, |\zeta(a)-\zeta(a')|^j.
\end{align*}
Now, choose $\lambda_\Delta > A$. Since the functions $R_r(z^{-1})$ are holomorphic on the disk $|z| > A$, we have $|R_{r,j}| \lesssim \lambda_\Delta^j$ over all $r \in \{1, \ldots, d-1\}$ and $j \in \{0, 1, 2, \ldots\}$, as mentioned earlier. It follows that
\begin{align*}
\sum_{j=0}^\infty \frac{|R_{r,j}|}{j!} \, |\zeta(a)-\zeta(a')|^j
& \lesssim \sum_{j=0}^\infty \frac{\lambda_\Delta^j}{j!} \, |\zeta(a)-\zeta(a')|^j \\
& \lesssim e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
\end{align*}
over all $a, a' \in \domain_\alpha^2$, so
\begin{align*}
|\softker^\alpha(a, a')| \lesssim \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} \sum_{r=0}^{d-1} |\zeta(a')|^r e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}.
\end{align*}
over all $a, a' \in \domain_\alpha^2$.
\color{RoyalBlue}
\begin{align*}
|k_R(a,a')| & \le \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{|R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(a)|}|\zeta(a')|^r \\
& \lesssim \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{\lambda_\Delta^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(a)|}|\zeta(a')|^r \\
& \lesssim \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} \sum_{r=0}^{d-1} |\zeta(a')|^r \sum_{j=0}^\infty \frac{\lambda_\Delta^j}{j!} \, |\zeta(a)-\zeta(a')|^j \\
& \lesssim |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(a)|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
& \lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(a)}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
& \lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(a)}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
\end{align*}
\color{black}
\textcolor{magenta}{[I'm pretty sure this is false, because $q(a')$ and $p(a)$ have independent arguments] $\langle$} now we notice that $\Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert$ is bounded for $a,a'$ far from $\alpha$ \textcolor{magenta}{$\rangle$} by the argument we use in the proof of Condition \eqref{cond:diag-basic}. If $\zeta(a), \zeta(a')$ are close to $\alpha$ we can use Condition \eqref{cond:sing}

@@

and $\gamma=1$.
\end{itemize}
\begin{brainstorm}
\item Show that $\hardpart^\alpha$ satisfies Condition~\eqref{cond:reg-p}.
\item Apply Prosposition~\ref{prop:alt-general_volterra} to get result.
\end{brainstorm}
\par\color{Tomato}
Finally, to get the result as stated, we need to show that
\[ f_{0, \alpha} \in \zeta^{\tau_\alpha - 1} + \singexpalg{\tau_\alpha}(\domain_\alpha). \]
Like in the proof of Proposition \ref{prop:alt-general_volterra}, it's enough to show that $p$ satisfies Condition \eqref{cond:reg-p} with $\epsilon=1$. Since $p$ is a polynomial with a simple zero at $\zeta=\alpha$, we have that
